On Secure Delegation of SampBQP with a Classical Client

### 2020-02-07 bqp.tex
Start writing FBQP

\section{Delegation for BQP}
\label{sec:BlindBQP}

@@

\Ethan{Cut into two subsections, one for BQP and one for FBQP}

In this section we present our constant-round blind delegation protocol for $\BQP$. That is, proving this theorem:
\begin{thm}
	\label{thm:QPIP0BQP}
	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}
We'll spend this section construct said protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.
We'll later construct a protocol for $\SampBQP$ following the same flow of logic, albeit requiring more careful analysis.

@@

	There exists $\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$ where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and polynomial-time algorithm $\widehat{\mathsf{QHE.Dec}}$ such that:
	$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
\end{thm}
\begin{proof}
	This is a proof by construction.
	We require $\Lambda'$ and $\widehat{\mathsf{QHE.Dec}}$ such that $\forall\sigma=(X^xZ^z\rho Z^zX^x, c_{x,z})$,
	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'(\sigma)$$

@@

	Note that the Pauli one-time pad on $u$ commutes with $X$ and $Z$ measurements.
	So let $\widehat{\mathsf{QHE.Dec}}$ decode $c_{x, z}$ to get $(x, z)$ and undo the one-time pad on $u$ to get $\Lambda(\rho)$.
\end{proof}

@@

\begin{thm}
	\cref{proto:BlindBQP} has negligible completeness and soundness.
\end{thm}
\begin{proof}
	The completeness follows by inspection.

@@

    \Ethan{rewrite the following as a reduction. If exists adversary $P*$ that breaks soundness of this protocol, it breaks the other one...}

	The verifier's actions, by \cref{decodeMeasureOrder}, is $\negl(n)$-close to to decoding $\sigma$ to get some $\rho$ then applying $\Lambda$ to get $w$.
	In other words, the verifier's outputs is $\negl(n)$-close to the verifer of \cref{proto:BQP} under the same input and receiving $\rho$ from the prover.
	So the conclusion follows from the negligible soundness of \cref{proto:BQP}.
\end{proof}

\begin{thm}
	\cref{proto:BlindBQP} is blind.
\end{thm}
\begin{proof}
	The only thing the prover sees is $c$ and $evk$, so this follows directly from $\mathsf{QHE}$'s security.
\end{proof}

\Ethan{Use google docs to replace below}

\cite{mahadev_delegation} gives a compiler from $\QPIP_1$ protocols of the form in \cref{proto:BQP} to $\QPIP_0$ but deteriorates soundness.
Note that \cref{proto:BlindBQP} can also be collapsed into the same form \Ethan{Actually specify QPIP1 one-message use only XZ measurements}, so the same compiler can also be applied to it to obtain a $\QPIP_0$ protocol.

We can then use results from \cite{parallelrep} to apply parallel repetition and recover the negligible soundness.

@@

\begin{protocol}{Blind and verifiable $\QPIP_0$ delegation for $\FBQP$}
	\label{QPIP0FBQP}
	Suppose $y\in\set{0,1}^m$ is the output of our $\FBQP$ instance.
	\begin{enumerate}
		\item Apply \cref{thm:QPIP0BQP} to every $y_i=0$ and $y_i=1$ case in parallel, resulting in a total of $2m$ cases.
		\item Output $y$ if for each $i$ precisely one of the $y_i=0$ and $y=i=1$ cases accepts.
	\end{enumerate}
\end{protocol}

\Ethan{TODO prove that \cref{QPIP0FBQP} actually works as expected}

>>>>

\section{Blind Delegation for BQP and FBQP}
\label{sec:BlindBQP}

@@

\Ethan{TODO Intro this section}

\subsection{Blind Delegation for BQP}
\label{subsec:BlindBQP}

In this subsection we present our constant-round blind delegation protocol for $\BQP$. That is, proving this theorem:
\begin{thm}
	\label{thm:QPIP0BQP}
	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}
We'll spend this section construct said protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.
We'll later construct a protocol for $\SampBQP$ following the same flow of logic, albeit requiring more careful analysis.

@@

	There exists $\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$ where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and polynomial-time algorithm $\widehat{\mathsf{QHE.Dec}}$ such that:
	$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
\end{thm}
\begin{prf}
	This is a proof by construction.
	We require $\Lambda'$ and $\widehat{\mathsf{QHE.Dec}}$ such that $\forall\sigma=(X^xZ^z\rho Z^zX^x, c_{x,z})$,
	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'(\sigma)$$

@@

	Note that the Pauli one-time pad on $u$ commutes with $X$ and $Z$ measurements.
	So let $\widehat{\mathsf{QHE.Dec}}$ decode $c_{x, z}$ to get $(x, z)$ and undo the one-time pad on $u$ to get $\Lambda(\rho)$.
\end{prf}

@@

\begin{thm}
	\cref{proto:BlindBQP} has negligible completeness and soundness.
\end{thm}
\begin{prf}
	The completeness follows by inspection.

@@

    \Ethan{rewrite the following as a reduction. If exists adversary $P*$ that breaks soundness of this protocol, construct $P**$ that breaks the other one...}

	The verifier's actions, by \cref{decodeMeasureOrder}, is $\negl(n)$-close to to decoding $\sigma$ to get some $\rho$ then applying $\Lambda$ to get $w$.
	In other words, the verifier's outputs is $\negl(n)$-close to the verifer of \cref{proto:BQP} under the same input and receiving $\rho$ from the prover.
	So the conclusion follows from the negligible soundness of \cref{proto:BQP}.
\end{prf}

\begin{thm}
	\cref{proto:BlindBQP} is blind.
\end{thm}
\begin{prf}
	The only thing the prover sees is $c$ and $evk$, so this follows directly from $\mathsf{QHE}$'s security.
\end{prf}

\Ethan{Below is copied from google docs}

Finally, we prove Thm 3.1 by applying Mahadev's measurement protocol~\cite{mahadev_delegation} to Protocol 3 to compile it into a $\QPIP_0$ protocol $(P', V')$ \Ethan{fix name}.
Note that Mahadev's measurement protocol can compile any $\QPIP_1$ protocol with X, Z measurement and negligible soundness to a $\QPIP_0$ protocol, and Protocol 3 is a $\QPIP_1$ protocol with X, Z measurement and negligible soundness.
Thus the resulting protocol $(P', V')$ is a O(1)-round $\QPIP_0$ protocol with soundness error $\frac{3}{4} + \negl$ \Ethan{Write what is it negl in}. (preserve blindness)

\Ethan{State compiled protocol and prove soundness that way}

\begin{protocol}{\Cref{proto:BlindBQP} compiled using Mahadev's measurement protocol}
	\label{proto:QPIP0BQP}
	TODO

\end{protocol}

We then apply the recent result parallel repetition to reduce soundness error...

\Ethan{cite both parallel rep papers}

\begin{protocol}{Parallel repetition of}
	\label{proto:repQPIP0BQP}
	Run $n$ copies of \cref{proto:QPIP0BQP} in parallel. Accept if...? TODO some kind of standard procedure here.

\end{protocol}

\subsection{Blind delegation of FBQP}

@@

Let $f\in\FBQP$.

Define the language $L_{f, i, b}$ s.t. $x\in L_{f, i, b}$ if the $i$th bit of $f(x)$ is $b$.

\begin{protocol}{Blind and verifiable $\QPIP_0$ delegation for $\FBQP$}
	\label{QPIP0FBQP}
	Input: $x\in\set{0, 1}^n$

	Suppose without loss of generality that the verifier knows $f(x)$ is of length $m=\poly(n)$ \Ethan{Seems like a strong assumption; maybe need to explain how}
	Let $\cL = \set{L_{f, i, b}: i\in[m], b\in\set{0, 1}}$
	\begin{enumerate}
		\item Run \cref{proto:repQPIP0BQP} for all languages $L\in\cL$ in parallel
		\item If $\exists i$ s.t. $x\in L_{f, i, 0}$ and $x\in L_{f, i, 1}$ gives the same output, reject.
		\item Otherwise, define $y_i = b$ where $x\in L_{f, i, b}$. This gives $y\in\set{0,1}^m$
		\item Verifier outputs $y$
	\end{enumerate}
\end{protocol}

\begin{theorem}
	\cref{QPIP0FBQP} has negligible completeness and soundness, and is blind.
\end{theorem}
\begin{prf}
	TODO
\end{prf}

### 2020-02-07 preliminaries.tex
Start writing FBQP

\Ethan{TODO Dfn $\BQP$}
\Ethan{TODO Negligible errors}

\begin{dfn}
	$\QMA$ is the quantum analogue of the class $\MA$. The verifier in $\QMA$ is now a $\BQP$ machine.
\end{dfn}

\begin{definition} [$\FBQP$]
	TODO copy from https://www.csa.iisc.ac.in/~chandan/courses/complexity15/notes/lec23.pdf and add in overwhelming prob.
\end{definition}

\begin{dfn}
    \Ethan{TODO Negligible errors}
	$\FBQP$ is the functional analogue of the class $\BQP$. That is, every instance corresponds to a string rather than a yes/no bit. The error probability is still bounded above away from $\fot$ for some uniform quantum circuit family.
\end{dfn}

>>>>

\begin{definition} [$\BQP$]
	\Ethan{TODO: Replace this with something that makes more sense}
	A language $L$ is in $\BQP$ if it can be decided by some uniform quantum circuit family.
\end{definition}

\begin{definition} [$\FBQP$]
	A function $f:\set{0,1}^*\rightarrow\set{0,1}^*$ is in $\FBQP$ if there is a $\BQP$ machine that, $\forall x$, outputs $f(x)$ with overwhelming probability.
\end{definition}
